\chapter{Related works}\label{chap: Related works}

There are official works on HD wallet for Secp256k1 that we would like to include. First of all is the \emph{BIP0032} \cite{github/bip0032}, a Bitcoin Improvement Proposal that describes hierarchical deterministic wallets. The specification is intended to set a standard for deterministic wallets that can be interchanged between different clients. Although the wallets described here have many features, not all are required by supporting clients. The specification consists of two parts. In a first part, a system for deriving a tree of key pairs from a single seed is presented. The second part demonstrates how to build a wallet structure on top of such a tree. The document explains clearly how they use HMAC-SHA512 to derive a child key. Also, they specify the wallet structure, its use cases and test vector to prove their work. In \cite{DBLP:Deterministic}, their super-wallet/sub-wallet is similar to a master key and a child key. They applied  the \emph{BIP0032} into their model to show a use case of its. However; the model is quite simple and, in a way, separates the master and child key.

On the other hand, for designing a wallet, there are some works mention about how a wallet is secure and the privacy of blockchain, for instance in \cite{DBLP:towards_blockchain}. They analyzed the wallet and constructs data privacy protection in system. They designed a complete architecture and implementation method of data efficient transaction, such as data three weight separation, data privacy isolation on the chain, cross network and cross cloud deployment algorithm decomposition multi center collaboration, as well as collaborative services on the chain and off the chain, focusing on the feasibility and simple and effective implementation.